### 2021-01-10 tex/paper.tex
Fix spelling.

Upon logging into a Simplifier instance, the user sees the Simplifier dashboard, seen in \cref{fig:simplifier_dashboard}. The dashboard provides an overview of all elements represented by tiles. The “Applications” tile opens a list of applications, allowing to edit them and create new ones. “Widgets” allows viewing existing building blocks and also creating new reusable components. “Connectors” allow specifying connections to external services, e.g. for sending emails or accessing a ReST API. The “Business Objects” tile is used to create workflows by assigning connectors, plugins and functions to business objects. The “Database Designer” is used for creating database schemas

@@

For our TODO List application, we first needed to create a connector to a database. Simplifier allows creating a connector to common MySQL, PostgreSQL and other databases. We opted for a \texttt{SQL} connector using the SQLite back end to avoid having to set up an external database server. Next, we opened the “Database Designer” and created a schema for a TODO list item, choosing the \texttt{SQL} connector we created as data source. The schema can then be edited using an entity-relationship (ER) diagram editor. We added a entity called \texttt{task} with fields for \texttt{status}, \texttt{title} and \texttt{body}. With a click of a button, we could then deploy the changes in the ER diagram to the database.

>>>>

Upon logging into a Simplifier instance, the user sees the Simplifier dashboard, seen in \cref{fig:simplifier_dashboard}. The dashboard provides an overview of all elements represented by tiles. The “Applications” tile opens a list of applications, allowing to edit them and create new ones. “Widgets” allows viewing existing building blocks and also creating new reusable components. “Connectors” allow specifying connections to external services, e.g. for sending emails or accessing a ReST API. The “Business Objects” tile is used to create workflows by assigning connectors, plugins and functions to business objects. There is also a “Database Designer” which is used for creating database schemas.

@@

For our TODO List application, we first needed to create a connector to a database. Simplifier allows creating a connector to MySQL, PostgreSQL and other common databases. We opted for a \texttt{SQL} connector using the SQLite back end to avoid having to set up an external database server. Next, we opened the “Database Designer” and created a schema for a TODO list item, choosing the \texttt{SQL} connector we created as data source. The schema can then be edited using an entity-relationship (ER) diagram editor. We added a entity called \texttt{task} with fields for \texttt{status}, \texttt{title} and \texttt{body}. With a click of a button, we could then deploy the changes in the ER diagram to the database.
